---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Step 1 Result

```{r}
library(classdata)
library(tidyverse)
head(ames)
```

```{r}
str(ames)
```

```{r}
summary(ames)
```

```{r}
?ames
```

There are 14 variables in this data set.

There is the house's "Style", how the house looks, which is a categorical factor type of data. In "Style" there are 6 options, detailing if the house is one or two story and other aspects of its design. There is an other option as well.

There is "Occupancy" which is the intended use which is categorical factor data type as well. There are 5 unique values with Condominium, Single-Family, Townhouse, Two-Family Conversion, and Two-Family Duplex.

There is "Sales Date" which is the date that the house sold and is a date data type. It ranges from July 3rd, 2017 to August 31st, 2022.

"Sale Price" is the price at which the house is sold in US Dollars and is a numerical data type. The range is 20.5 million with a minimum house sale price of 0 (likely never sold the house) and a maximum of 20,500,000. 20,500,000 is an outlier and the interquartile range is 119,100 between 170,900 to 280,000.

"MultiSale" is a logical data type with NA (Not a MultiSale) and Y (Yes a Multisale) as the two unique values. It measures whether or not a house was sold in a "package" likely alongside another house.

"YearBuilt" is an integer variable and numerical data type. This measures the year that the house was built. The years built ranges 66 years between 1956 to 2022. Some have a 0 or are NA. They likely did not record this data.

"Acres" is a numerical data type and measures the number of acres of the lot the house is on. The interquartile range is 0.1268 acres between 0.1502 and 0.2770 with a minimum of 0 and a maximum of 12.0120. The houses with 0 acres are only the buildings and do not include the land it is attached to.

"Total Living Area" is a numerical data type and the total square footage of a house's living area, in other words, the inside of the house. The interquartile range is 697 square feet between 1095 and 1792 with a minimum of 0 and maximum of 6007. Those houses with 0 sf of total living area likely do not have any buildings and is just the selling of an empty plot of land.

"Bedrooms" is a numerical data type showing the number of bedrooms in a house. It has a range of 10 bedrooms from 0 to 10.

"FinishedBsmtArea" is a numerical data type showing the total square footage of a house's basement area. It has a range of 6,486 square feet from 10 to 6,496. It is important to note that no houses are marked as zero. Either every house has a basement or those without basements are marked NA.

"Lot Area" is a numerical data type showing the total square footage of a house's entire lot. It has an interquartile range of 5,535 square feet from 6,553 to 12,088 with a minimum of 0 (same reasoning as for the 0s in "Acres") and a maximum of 523,228.

"AC" is a logical data type with "Yes" and "No" meaning a house has AC or does not respectively.

"FirePlace" is a logical data type with "Yes" and "No" meaning a house has a Fire Place or does not respectively.

"Neighborhood" is a categorical data type describing the location of the house in Ames based on the neighborhood it is in. There are about 42 unique values.

# Step 2 Result

Price is the variable of interest since it is the output that we want to predict or model based on the other factors

# Step 3 Result

Which variable is the main variable?

Price

What is the range of this variable?

```{r}
range(ames$`Sale Price`, na.rm = TRUE)
```

Draw a histogram for a numeric variable or a bar chart, if the variable is categorical.

```{r}
  ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(bins = 50, fill = "skyblue", color = "black") +
  labs(x = "Sales Price", y = "Count", title="Count of Houses by Price")
ames |>
  filter(`Sale Price` != 0) |>
  ggplot(aes(x = log(`Sale Price`))) +
  geom_histogram(bins = 50, fill = "skyblue", color = "black") +
  labs(x = "Sales Price (log)", y = "Count", title="Count of Houses by Price (log scale)")
```

What is the general pattern?

Extremely right skewed.

Is there anything odd?

High concentration near 0 because many of the houses haven't been sold.

```{r}
sum(ames$`Sale Price` == 0)
```

# Step 4 Result

Henry:

The variable I chose was Total Living Area, since when filtering out Condominiums and 1 Story Frames and unsold properties, it correlated pretty tightly with price.


```{r}
ames |>
  filter(`Sale Price` != 0, Style != "1 Story Frame", Occupancy != "Condominium") |>
  ggplot(aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) +
  geom_point(alpha = 0.4)
```

Alexander:

"Bedrooms" is my variable of choice as I believe the number of bedrooms will directly influence the final sale price of the house. "Bedrooms" has a range of 10 bedrooms between 0 and 10 with an interquartile range of 1 between 3 and 4 bedrooms.

```{r, Bedrooms Histogram}
ames |>
  ggplot(aes(x = Bedrooms)) +
  geom_histogram(bins = 10)
```

```{r, Price by Bedrooms}
ames |>
  filter(`Sale Price` != 0) |>
  group_by(Bedrooms) |>
  summarize(Mean_price = mean(`Sale Price`, na.rm = TRUE)) |>
  ggplot(aes(x = Bedrooms, y = Mean_price)) +
  geom_bar(stat = 'identity')
```

This bar chart shows how for each number of bedrooms what the average price of the house is. Houses with only 1 bedroom seem to have a significantly higher house price. One would assume that as the number of bedrooms increase the price of the house will increase, however this is not the case. It may be important to look at total square footage to get a more accurate look into how price is affected. I also filtered out houses that did not sell and the result was still the same. 
=======
>>>>>>> 4c40b7a202ef77252e172c54145199ab32b043ff
