---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Step 1 Result

```{r}
library(classdata)
library(tidyverse)
head(ames)
```
```{r}
str(ames)
```
```{r}
summary(ames)
```


# Step 2 Result
Price is the variable of interest since it is the output that we want to predict or model based on the other factors


# Step 3 Result
Which variable is the main variable?

Price

What is the range of this variable?
```{r}
range(ames$`Sale Price`, na.rm = TRUE)
sum(ames$`Sale Price` == 0)
```

Draw a histogram for a numeric variable or a bar chart, if the variable is categorical.

```{r}
  ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(bins = 50, fill = "skyblue", color = "black") +
  labs(x = "Sales Price", y = "Count", title="Count of Houses by Price")
ames |>
  filter(`Sale Price` != 0) |>
  ggplot(aes(x = log(`Sale Price`))) +
  geom_histogram(bins = 50, fill = "skyblue", color = "black") +
  labs(x = "Sales Price (log)", y = "Count", title="Count of Houses by Price (log scale)")
```

What is the general pattern?

Extremely right skewed.

Is there anything odd?

High concentration near 0 because many of the houses haven't been sold.

# Step 4 Result
